Response to the defense feedback

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

We use the chi-squared test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r \cdot c$ two-way contingency table. The chi-squared test statistic and the degrees of freedom $v$ are calculated with the formula below.
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad and	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

>>>>

We use the chi-squared test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r \cdot c$ two-way contingency table. The chi-squared test statistic and the degrees of freedom $v$ are calculated with the formula below.
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}, \qquad 	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
